CrypTool Skript \\ Mathematik und Kryptographie

### 2002-06-26 script/de/chapters/numbertheory.tex
no message

Zum Zeitpunkt der Erstellung dieses Kapitels (Mai 2002) war mir nichts dar"uber bekannt,
inwieweit die im Bernstein-Papier vorgeschlagenen theoretischen Ansatzes realisiert wurden oder
wieweit die Finanzierung seines Forschungsprojektes ist.

>>>>

Arjen Lenstra, Adi Shamir et. al. haben das Bernstein-Paper analysiert (siehe
\href{http://www.cryptosavvy.com/mesh.pdf}{\tt http://www.cryptosavvy.com/mesh.pdf}).
Als Ergebnis kommen Sie zu einer Bitl"angen-Verbesserung der Faktorisierung um den Faktor 1.17 
(anstatt Faktor 3 wie von Bernstein erwartet).

Die Zusammenfassung ihres Papers ``Analysis of Bernstein's Factorization Circuit'' lautet:

``In [1], Bernstein proposed a circuit-based implementation of
the matrix step of the number field sieve factorization algorithm. We
show that under the non-standard cost function used in [1], these circuits
indeed offer an asymptotic improvement over other methods but
to a lesser degree than previously claimed: for a given cost, the new
method can factor integers that are 1.17 times larger (rather than 3.01).
We also propose an improved circuit design based on a new mesh routing
algorithm, and show that for factorization of 1024-bit integers the
matrix step can, under an optimistic assumption about the matrix size,
be completed within a day by a device that costs a few thousand dollars.
We conclude that from a practical standpoint, the security of RSA relies
exclusively on the hardness of the relation collection step of the number
field sieve.''

Auch \href{http://www.rsasecurity.com}{RSA Security} kommt in ihrer Analyse der Bernstein Arbeit, mit dem Titel
{\em Has the RSA algorithm been compromised as a result of Bernstein's Paper?} (vom 8. April 2002), 
zu dem Ergebnis, das RSA weiterhin als ungebrochen betrachtet werden kann (siehe
\href{http://www.rsasecurity.com/}{\tt http://www.rsasecurity.com}).
